OpenMPIR

### 2017-09-07 paper.tex
Added citations

\section{Introduction}

@@

This work has \emph{only been on the frontend}, which means we use the only
existing backend for Tapir, which generates code that calls into the Cilk
runtime, \texttt{libcilkrts}. This has implications for adhering to the OpenMP
specification. For example, environment variables such as
\texttt{OMP\_NUM\_THREADS} are ignored, replaced by \texttt{CILK\_NWORKERS}.
We discuss some of these issues below, and return to address others in the
future work section.

@@

In this section we discuss the results of running our evaluation on our
implementation, and how its performance compared to the existing
implementations listed in Section~\ref{Sec:Evaluation}. See
Figure~\ref{Fig:results} for a simple visualization of the performance. Each
graph represents a single benchmark from the previously enumerated Barcelona
benchmarks, and each bar represents one of the implementations.

\begin{figure*}
\begin{multicols}{2}
  \includegraphics[width=\linewidth]{alignment.pdf} \par
  \includegraphics[width=\linewidth]{fib.pdf} 
  \includegraphics[width=\linewidth]{fft.pdf} \par
  \includegraphics[width=\linewidth]{floorplan.pdf} 
  \includegraphics[width=\linewidth]{sort.pdf} \par
  \includegraphics[width=\linewidth]{nqueens.pdf}
\end{multicols}
\caption{Barcelona OpenMP Task Suite Results}
\end{figure*}

\begin{figure*}
\begin{multicols}{2}
  \includegraphics[width=\linewidth]{health.pdf} \par
  \includegraphics[width=\linewidth]{sparselu.pdf} 
\end{multicols}
\centering
\includegraphics[width=0.45\linewidth]{strassen.pdf}
\caption{Barcelona OpenMP Task Suite Results (continued)}
\end{figure*}

@@

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require careful knowledge of each of the frontends and runtimes. One thing we
can guess at is that despite the focus of the paper, \emph{IR optimisations are
unlikely to be the cause of performance improvements}. Our evidence for this
comes from Shardl et al. \cite{}. While some IR optimisations have been
implemented, they seem to have significantly more effect on parallel loop code,
while the tasking code remains relatively unaffected by IR optimizations
\cite{}.

@@

While OpenMP and Cilk have similar fork-join style semantics that Tapir
implements naturally, many allow a more flexible mechanism for synchronization:
futures \cite{qthreads, hpx, chapel, charm++}. The primary difference
between the fork-join parallelism represented by Tapir and these approaches
is that \emph{child tasks can outlive their parents}. Figuring out how
to represent this class of parallelism in Tapir represents a significant
challenge for future work.

@@

A third approach is to have a separate instruction set for parallelism. This is
the approach taken by projects like HPIR \cite{}, SPIRE \cite{}, and INSPIRE
\cite{}. This approach has the downside of being unable to re-use existing
optimization and analysis infrastructure of an existing IR.

>>>>

\section{Introduction} \label{Sec:Introduction}

@@

This work represented in this paper is only frontend implementation, which
means we use the only existing backend for Tapir. The existing backend
generates code that calls into the Cilk runtime, \texttt{libcilkrts}. This has
implications for adhering to the OpenMP specification. For example, environment
variables such as \texttt{OMP\_NUM\_THREADS} are ignored, replaced by
\texttt{CILK\_NWORKERS}.  We discuss some of these issues below, and return to
address others in the future work section.

@@

In this section we discuss the results of running our evaluation on our
implementation, and how its performance compared to the existing
implementations listed in Section~\ref{Sec:Evaluation}. See
Figures~\ref{Fig:results} and \ref{Fig:results2} for a simple visualization of
the performance. Each graph represents a single benchmark from the previously
enumerated Barcelona benchmarks, and each bar represents one of the
implementations.

\begin{figure*}
\begin{multicols}{2}
  \includegraphics[width=\linewidth]{alignment.pdf} \par
  \includegraphics[width=\linewidth]{fib.pdf} 
  \includegraphics[width=\linewidth]{fft.pdf} \par
  \includegraphics[width=\linewidth]{floorplan.pdf} 
  \includegraphics[width=\linewidth]{sort.pdf} \par
  \includegraphics[width=\linewidth]{nqueens.pdf}
\end{multicols}
\caption{Barcelona OpenMP Task Suite Results}
\label{Fig:results}
\end{figure*}

\begin{figure*}
\begin{multicols}{2}
  \includegraphics[width=\linewidth]{health.pdf} \par
  \includegraphics[width=\linewidth]{sparselu.pdf} 
\end{multicols}
\centering
\includegraphics[width=0.45\linewidth]{strassen.pdf}
\caption{Barcelona OpenMP Task Suite Results (continued)}
\label{Fig:results2}
\end{figure*}

@@

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require careful knowledge of each of the frontends and runtimes. One thing we
can guess at is that despite the focus of the paper, \emph{IR optimisations are
unlikely to be the cause of performance improvements}. Our evidence for this
comes from Shardl et al. \cite{tapir}. While some IR optimisations have been
implemented, they seem to have significantly more effect on parallel loop code,
while the tasking code remains relatively unaffected by IR optimizations
\cite{tapir}.

@@

While OpenMP and Cilk have similar fork-join style semantics that Tapir
implements naturally, many allow a more flexible mechanism for synchronization:
futures \cite{qthreads, chapel, hpx}. The primary difference between the
fork-join parallelism represented by Tapir and these approaches is that
child tasks can outlive their parents. Figuring out how to represent this class
of parallelism in Tapir represents a significant challenge for future work.

@@

A third approach is to have a separate instruction set for parallelism. This is
the approach taken by projects like HPIR \cite{zhao2011intermediate}, SPIRE
\cite{khaldi2012spire}, and INSPIRE \cite{jordan2013inspire}. This approach has
the downside of being unable to re-use existing optimization and analysis
infrastructure of an existing IR.
